---
title: "Sun Haven: More Mana"
author: '"Phung (foom) Tran"'
output: 
  slidy_presentation: 
    css: custom.css
    geometry: margin=1in   # Page margins
  
---
# Introduction

```
Sun Haven is a farming rpg similar to more popular titles such as Stardew Valley and Harvest Moon. Players must balance there time between farming, crafting, and exploration to improve their farm and player stats. By permanently boosting your stats, such as mana, players can optimize there gameplay. 

```
```{r Intro for Final Paper, eval=FALSE, include=FALSE}
# To permanently boost your mana stat, there are many events or random objects that the player can find. However, the most mainline way to do this would be to eat. Whether it be foragables or cooked foods, eating is the most basic way to raise mana, making it important to manage your resources. Specifically because having more mana let's you cast spells that make farming/combat and traveling more efficient.
# 
# Whether its after the first year of game play or beginning of the game, having this information will save resources for making more storage containers and saves space in your home. Just like other games in this genre, you need supplies and space to create the storage. While the game might give you three homes/farms to travel through, those same resources can be used for other crafts such as weapons/armor and furnace materials. 
# 
# It can be hard to keep track of what foods are the most ideal to constantly stack up on. This also means you have to mine more ore and wood, with wood specifically needing more time to regrow. By looking through the charts presented, we can get useful knowledge about how to proceed with resource management to increase mana to optimize game play
```

# Questions I wanted to ask

  1. What are some crops or cooked foods that we can focus on in Spring and starting town? 
  2. After first year gameplay,  what can players focus on in Spring to see what can be   prepared to boost our mana?
  3. What cooked foods give us the biggest amounts of mana? 


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)

```

```{r Installed_Packages, message=FALSE, warning=FALSE, include=FALSE}

install.packages("janitor", repos = "https://cloud.r-project.org/") # Used to clean up cvs files
install.packages("wesanderson", repos = "https://cloud.r-project.org/") # wes anderson color palettes
install.packages("extrafont", repos = "https://cloud.r-project.org/") # more fonts to choose from 
install.packages("gridExtra", repos = "https://cloud.r-project.org/") # Used to make 2x2 graphs because plotly is being used 
install.packages("cowplot", repos = "https://cloud.r-project.org/") # Used to extract legend from a plot and place on 2x2 grid 

# had to use repos = , in order to knit docuemnt. 

```

---

```{r Libraries, echo=TRUE, warning=FALSE}

# Loading libraires used

library(tidyverse) # Loads R packages fro data manipulation and visualization
library(ggplot2) # Used to create graphs/charts
library(janitor) # Used to help clean data 
library(wesanderson) # Color palettes from Wes Anderson movies 
library(extrafont) # Loaded in more fonts 
library(gridExtra) # Create a 2x2 grid for plots
library(grid) # Used to change font for gridExtra
library(cowplot) # Clean

```

```{r include=FALSE}

font_import() # import in more font options
loadfonts() # load all font options 

```

---

```{r CSV_Files, echo=TRUE}

# Loading in data that will be used

cooked_food <- read.csv('Sun Haven Cooked Food.csv') 

animal_product <- read.csv('Sun Haven Farm Animal.csv')

fish <- read.csv("Sun Haven Fish.csv")

foragables <- read.csv('Sun Haven Foragables.csv')

crops <- read.csv('Sun Haven Crops.csv')

```

```{r Clean_files, include=FALSE}

# change "." and spaces in column names to _

cooked_food <- cooked_food %>% 
  clean_names()

foragables <- foragables %>% 
  clean_names()

animal_product <- animal_product %>%
  clean_names()

crops <- crops %>% 
  clean_names()

fish <- fish %>% 
  clean_names()

```

--- 

```{r include=FALSE}

# Double checking column names

colnames(cooked_food)
colnames(crops)
colnames(foragables)
colnames(animal_product)

# crops <- crops %>% select(-c(X, X.1, X.2)) # Deleted extra columns in csv file

```


```{r echo=TRUE, eval=TRUE}


# Convert all columns to character, clean missing values ("", "N/A", "N A"), and process numeric columns

cooked_food <- cooked_food %>%
  mutate(across(everything(), as.character)) %>%
  mutate(across(everything(), ~ na_if(., ""))) %>% # for string values
  mutate(sell_price = as.numeric(sell_price), # convert any number columns into numeric
         mp = as.numeric(mp),
         hp = as.numeric(hp)) %>%  
  mutate(across(where(is.character), ~ na_if(., "N/A"))) %>%  # Replace "N/A" with NA
  mutate(across(where(is.character), ~ na_if(., "N A"))) %>%   # Replace "N A" with NA 
  mutate(across(where(is.character), ~ gsub("amount", "", .)))  # Remove "amount"

```
 
```{r include=FALSE}

foragables <- foragables %>%
  mutate(across(everything(), as.character)) %>%
  mutate(across(everything(), ~ na_if(., ""))) %>%
  mutate(sell_price = as.numeric(sell_price),
         mp = as.numeric(mp),
         hp = as.numeric(hp)) %>%
  mutate(across(where(is.character), ~ na_if(., "N/A"))) %>%
  mutate(across(where(is.character), ~ na_if(., "N A")))


animal_product <- animal_product %>%
  mutate(across(everything(), as.character)) %>%
  mutate(across(everything(), ~ na_if(., ""))) %>%
  mutate(sell_price = as.numeric(sell_price),
         mp = as.numeric(mp),
         hp = as.numeric(hp)) %>%
  mutate(across(where(is.character), ~ na_if(., "N/A"))) %>%
  mutate(across(where(is.character), ~ na_if(., "N A")))


crops <- crops %>%
  mutate(across(everything(), as.character)) %>%
  mutate(across(everything(), ~ na_if(., "N/A"))) %>%
  mutate(across(everything(), ~ na_if(., "N A"))) %>%
  mutate(sell_price = str_trim(sell_price)) %>%
  mutate(sell_price = as.numeric(sell_price),
         seed_price = as.numeric(seed_price),
         growth_time = as.numeric(growth_time),
         yield = as.numeric(yield),
         max_harvest = as.numeric(max_harvest),
         profit_per_day = as.numeric(profit_per_day))


fish <- fish %>%
  mutate(across(everything(), as.character)) %>%
  mutate(across(everything(), ~ na_if(., ""))) %>%
  mutate(across(where(is.numeric), as.numeric)) %>%
  mutate(sell_price = as.numeric(sell_price),
         mp = as.numeric(mp),
         hp = as.numeric(hp)) %>%
  mutate(across(where(is.character), ~ na_if(., "N/A"))) %>%
  mutate(across(where(is.character), ~ na_if(., "N A")))

```

```{r Spring_Crops_in_Sun_Haven, include=FALSE}

# Filtered plot sell prices and seed prices for Spring crops in Sun Haven, with lines and points for both prices

pal <- wes_palette("FantasticFox1", 5, type = "discrete")

sun_haven_crops <- crops %>% 
  filter(town == "Sun Haven", season == "Spring") %>% 
  filter(!is.na(sell_price))

max_price <-  max(crops$sell_price, na.rm = TRUE)

sun_haven_spring <- ggplot(sun_haven_crops, aes(x = name)) + 
  geom_line(aes(y = sell_price,
                group = 1, 
                color = "Sell Price"), 
            size = 1) +
  geom_point(aes(y = sell_price, 
                 color = "Sell Price")) +
  geom_line(aes(y = seed_price,group = 1, 
                color = "Seed Price"), 
                linetype = "dashed", size = 1) +
   geom_point(aes(y = seed_price,
                  color = "Seed Price")) +
  coord_flip() +
  scale_y_continuous(breaks = seq(from = 0,
                                  to = max_price,
                                  by = 80)) +
  scale_x_discrete(expand = expansion(add = c(1,1))) + # Adds space on both sides of the x-axis labels. Discrete because it's a str)
   scale_color_manual(values = c("Sell Price" = pal[1], 
                                "Seed Price" = pal[2])) + 
  labs(
    title = "Sun Haven (Spring)",
    subtitle = "Currency: Gold",
    x = "Crop Name",
    y = NULL) +
   theme(axis.title.x = element_text(margin = margin(t = 10), 
                                family = "Courier New", 
                                face = "bold"), # Move x-axis label downward
    axis.title.y = element_text(margin = margin(r = 10), 
                                family = "Courier New", 
                                face = "bold"), # Move y-axis label to the left
    axis.text.x = element_text(family = "Courier New"), # Set font for x-axis
    axis.text.y = element_text(family = "Courier New"),
    plot.title = element_text(
      vjust = 1,   # Move the title upward
      family = "Courier New", # Change font
      face = "bold",    # Make the title bold
      size = 16), # Adjust title size
    plot.subtitle = element_text(family = "Courier New"),
    legend.position = "none")
  
print(sun_haven_spring)

```


```{r Any_Season_Crops_in_Sun_Haven, include=FALSE}

# Filtered plot sell prices and seed prices for crops grown in "Any" season in Sun Haven, with lines and points for both prices

sun_haven_crops_any <- crops %>% 
  filter(town == "Sun Haven", 
         season == "Any", 
         category != "Flower",
         category != "Tree")

# Calculate the maximum price for setting y-axis breaks

max_price <- max(sun_haven_crops_any$sell_price, na.rm = TRUE)

# Create the plot for Sun Haven crops (Any season)

pal <- wes_palette("FantasticFox1", 5, type = "discrete")

sun_haven_any <- ggplot(sun_haven_crops_any, aes(x = name)) + 
  geom_line(aes(y = sell_price,
                group = 1, 
                color = "Sell Price"), 
            size = 1) +
  geom_point(aes(y = sell_price,
                 color = "Sell Price")) +
  geom_line(aes(y = seed_price,group = 1, 
                color = "Seed Price"), 
                linetype = "dashed", size = 1) +
   geom_point(aes(y = seed_price, 
                  color = "Seed Price")) +
  coord_flip() +
  scale_y_continuous(breaks = seq(from = 0, to = max_price, by = 40)) +
  scale_x_discrete(expand = expansion(add = c(1,1))) + # Adds space on both sides of the x-axis labels. Discrete because it's a str)
  scale_color_manual(values = c("Sell Price" = pal[1], 
                                "Seed Price" = pal[2])) + 
  labs(
    title = "Sun Haven (Any)",
    subtitle = "Currency: Gold",
    x = NULL, # Removes label on axis
    y = NULL) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x = element_text(family = "Courier New"), # Set font for x-axis
        axis.text.y = element_text(family = "Courier New"),  # Set font for y-axis
    plot.title = element_text(
      vjust = 1,   # Move the title upward
      family = "Courier New", # Change font
      face = "bold",    # Make the title bold
      size = 16), # Adjust title size
      plot.subtitle = element_text(family = "Courier New"),
    legend.title = element_text(family = "Courier New", face = "bold", size = 10),  # Change legend title font
    legend.text = element_text(family = "Courier New", size = 8))  # Change legend text font
  

print(sun_haven_any)

```

```{r Any_Season_Crops_in_Withergate, include=FALSE}

# Filtered plot sell prices and seed prices for crops grown in "Any" season in Withergate, with lines and points for both prices

withergate_crops <- crops %>% 
  filter(town == "Withergate", 
         season == "Any",
         category != "Tree")

# Calculate the maximum price for setting y-axis breaks

max_price <- max(withergate_crops$sell_price, na.rm = TRUE)

# Create the plot for Withergate crops

pal <- wes_palette("FantasticFox1", 5, type = "discrete")

withergate_any <- ggplot(withergate_crops, aes(x = name)) + 
  geom_line(aes(y = sell_price,
                group = 1,
                color = "Sell Price"), size = 1) +
  geom_point(aes(y = sell_price, color = "Sell Price")) +
  geom_line(aes(y = seed_price,group = 1, 
                color = "Seed Price"), 
                linetype = "dashed", size = 1) +
   geom_point(aes(y = seed_price, color = "Seed Price")) +
  coord_flip() +
  scale_y_continuous(breaks = seq(from = 0, to = max_price, by = 10)) +
  scale_x_discrete(expand = expansion(add = c(1,1))) + # Adds space on both sides of the x-axis labels. Discrete because it's a str)
  scale_color_manual(values = c("Sell Price" = pal[1], 
                                "Seed Price" = pal[2])) + 
  labs(
    title = "Withergate",
    subtitle = "Currency: Tickets",
    x = "Crop Name",
    y = "Sell Price vs Seed Price") +
  theme(axis.title.x = element_text(margin = margin(t = 10), 
                                family = "Courier New", 
                                face = "bold"), # Move x-axis label downward
    axis.title.y = element_text(margin = margin(r = 10), 
                                family = "Courier New", 
                                face = "bold"), # Move y-axis label to the left
    axis.text.x = element_text(family = "Courier New"), # Set font for x-axis
    axis.text.y = element_text(family = "Courier New"),
    legend.position = "none",
    plot.title = element_text(
      vjust = 1,   # Move the title upward
      family = "Courier New", # Change font
      face = "bold",    # Make the title bold
      size = 16), # Adjust title size)  
      plot.subtitle = element_text(family = "Courier New"))
 
print(withergate_any)

```

```{r Any_Season_Crops_in_NelVari, include=FALSE}

# Filtered plot sell prices and seed prices for crops grown in "Any" season in Nel'Vari, with lines and points for both prices

# Filter data for NelVari crops
NelVari_crops <- crops %>% 
  filter(town == "NelVari", 
         season == "Any",
         category != "Tree")

# Calculate the maximum price for setting y-axis breaks
max_price <- max(NelVari_crops$sell_price, na.rm = TRUE)

# Define color palette
pal <- wes_palette("FantasticFox1", 5, type = "discrete")

# Create the plot for NelVari crops
NelVari_any <- ggplot(NelVari_crops, aes(x = name)) + 
  geom_line(aes(y = sell_price, color = "Sell Price", group = 1), size = 1) +
  geom_point(aes(y = sell_price, color = "Sell Price")) +
  geom_line(aes(y = seed_price, color = "Seed Price", group = 1), linetype = "dashed", size = 1) +
  geom_point(aes(y = seed_price, color = "Seed Price")) +
  coord_flip() +  # Flip coordinates
  scale_y_continuous(breaks = seq(from = 0, to = max_price, by = 10)) +
  scale_x_discrete(expand = expansion(add = c(1,1))) +  # Adds space on both sides of the x-axis labels
  scale_color_manual(values = c("Sell Price" = pal[1], "Seed Price" = pal[2])) + 
  labs(
    title = "NelVari",
    subtitle = "Currency: Doubloons",
    x = NULL,   # Gets rid of label on x axis
    y = "Sell Price vs Seed Price"
  ) +
  theme(
    axis.title.x = element_text(margin = margin(r = 10), family = "Courier New", face = "bold"), # Move y-axis label to the left
    axis.text.x = element_text(family = "Courier New"), # Set font for x-axis
    axis.text.y = element_text(family = "Courier New"), # Set font for y-axis
    plot.title = element_text(vjust = 1, family = "Courier New", face = "bold", size = 16), # Adjust title size
    plot.subtitle = element_text(family = "Courier New"),
    legend.title = element_text(family = "Courier New", face = "bold", size = 10),
    legend.text = element_text(family = "Courier New", size = 8),
    legend.position = "bottom"  # Position legend at the bottom
  )

# Print the plot
print(NelVari_any)

```

---

```{r Plots_for_crops, echo=FALSE}


# Create the grid layout for the plots without overlapping

# Extract the legend from the modified plot (set to 'bottom')
shared_legend <- get_legend(NelVari_any)

# Remove the legend from individual plots
NelVari_any <- NelVari_any + theme(legend.position = "none")
sun_haven_any <- sun_haven_any + theme(legend.position = "none")

  
grid.arrange(
  # Arrange the plots in a 2x2 grid
  arrangeGrob(
    sun_haven_spring,     # Plot 1
    sun_haven_any,        # Plot 2
    withergate_any,       # Plot 3
    NelVari_any,          # Plot 4
    ncol = 2,             # 2 columns
    nrow = 2              # 2 rows
  ),
  # Add the shared legend at the bottom
  shared_legend,
  ncol = 1,  # Arrange the grid and legend vertically
  heights = c(4, 0.5))  # Adjust relative height of the grid 


```


These charts help us narrow down what crops we can grow if we just started the game. Specifically looking at fig.1 and fig.2. Fig. 3 and 4 are more useful when have gone through the first year of game play. While money is not the main thing we're looking for in the data, it is useful information to help decide a starting point.


---


Next, we can look at all the stations that is used to cook food.
You can tell that the starting station, cooking pot, has the most recipes that are available to you at the beginning of the game. By looking at this chart, you're starting town, Sun Haven, has more recipes for you to choose from.


```{r Station_Recipes_in_each_one, echo=FALSE}

# Define two color palettes

pal1 <- wes_palette("FrenchDispatch", 5, type = "discrete")  # First palette
pal2 <- wes_palette("FantasticFox1", 5, type = "discrete")  # Second palette

# Combine both palettes

combined_pal <- c(pal1, pal2)

# Create a lollipop chart showing the number of recipes in each cooking station

cooked_food_stations <- cooked_food %>% 
  group_by(station) %>% 
  summarise(count = n()) %>% 
  ggplot(aes(x = reorder(station, count), 
             y = count)) + 
           geom_segment(aes(xend = station,
                            y = 0, 
                            yend = count), 
                            color = "orange") +
           geom_point(aes(color = count),
                      size = 4, 
                      show.legend = FALSE) +
  scale_color_gradientn(colors = combined_pal) +
  coord_flip() +
  labs(
    title = "Cooking Stations: Recipes",
    x = "Station",
    y = "Amount of Recipes") +
   theme(
    legend.position = "none",
    axis.title.x = element_text(margin = margin(t = 10), 
                                family = "Courier New", 
                                face = "bold"), # Move x-axis label downward
    axis.title.y = element_text(margin = margin(r = 10), 
                                family = "Courier New", 
                                face = "bold"), # Move y-axis label to the left
    axis.text.x = element_text(family = "Courier New"), # Set font for x-axis
    axis.text.y = element_text(family = "Courier New"),  # Set font for y-axis
    plot.title = element_text(
      vjust = 1,   # Move the title upward
      family = "Courier New", # Change font
      face = "bold",    # Make the title bold
      size = 16)) # Adjust title size)  

print(cooked_food_stations)

```

---

```{r Cooked_Food_Mana_Stat_Boost, echo=FALSE}

# Define a discrete color palette (not continuous)

# Define two color palettes

pal1 <- wes_palette("FrenchDispatch", 5, type = "discrete")  # First palette
pal2 <- wes_palette("FantasticFox1", 5, type = "discrete")  # Second palette

# Combine both palettes
combined_pal <- c(pal1, pal2)

cooked_food_stats_mana <- cooked_food %>% 
  filter( stat == "Mana") %>% 
  group_by(station) %>%
  summarize(count = n()) %>%  # Count the number of cooked foods per station
  ggplot(aes(x = station, 
             y = count, 
             fill = station)) +
  geom_col() +
  scale_fill_manual(values = combined_pal) +
  labs(
    title = "Cooked Foods that Boost Mana",
    x = "Station",
    y = "Count of Foods") +
    theme(
    legend.position = "none",
    axis.title.x = element_text(margin = margin(t = 10), 
                                family = "Courier New", 
                                face = "bold"), # Move x-axis label downward
    axis.title.y = element_text(margin = margin(r = 10), 
                                family = "Courier New", 
                                face = "bold"), # Move y-axis label to the left
    axis.text.x = element_text(family = "Courier New"), # Set font for x-axis
    axis.text.y = element_text(family = "Courier New"),  # Set font for y-axis
    plot.title = element_text(
      vjust = 1,   # Move the title upward
      family = "Courier New", # Change font
      face = "bold",    # Make the title bold
      size = 16)) # Adjust title size) 

print(cooked_food_stats_mana)

```


By narrowing it down to only looking at recipes that permanently boost your mana, we can see that the cooking pot still has the most options available to you.


---

```{r Amount_of_Mana, echo=FALSE, warning=FALSE}

pal <- wes_palette("FantasticFox1", 5, type = "discrete")  # Second palette

cooked_food_stats_mana_amount <- cooked_food %>% 
  filter(stat == "Mana", station == "Cooking Pot") %>% 
  group_by(stat_boost) %>% 
  summarise(count = n()) %>% 
  ggplot((aes(x = stat_boost,
              y = count,
              fill = stat_boost))) +
  geom_col() +
  scale_fill_manual(values = pal) +
  labs(
    title = "Amount of Mana Boost in Cooking Pot Recipes",
    x = "Amount of Mana",
    y = "Amount of foods") +
   theme(
    legend.position = "none",
    axis.title.x = element_text(margin = margin(t = 10), 
                                family = "Courier New", 
                                face = "bold"), # Move x-axis label downward
    axis.title.y = element_text(margin = margin(r = 10), 
                                family = "Courier New", 
                                face = "bold"), # Move y-axis label to the left
    axis.text.x = element_text(family = "Courier New"), # Set font for x-axis
    axis.text.y = element_text(family = "Courier New"),  # Set font for y-axis
    plot.title = element_text(
      vjust = 1,   # Move the title upward
      family = "Courier New", # Change font
      face = "bold",    # Make the title bold
      size = 16)) # Adjust title size) 


print(cooked_food_stats_mana_amount)

```

From here, we can see the cooking pot has bias towards "small" stat boost available to us. However, we can also see that we do have recipes that give us "huge" permanent stat boost

---

```{r Huge_Stat_Boost_for_Cooking_Pot, echo=FALSE}

huge_mana <- cooked_food %>% 
  filter(stat == "Mana",
         station == "Cooking Pot", 
         stat_boost == "huge") %>% 
  arrange(desc(mp)) %>% 
  select(station, item,currency, stat, stat_boost, ingredient_1, ingredient_2, ingredient_3)


tibble(huge_mana)

```


These "huge" mana stat boost items contain "Golden" in the name as well as ingredients listed that are not possible to obtain early on. With the currency being "Mana Orb", the town Nel'Vari would have to be available to the player.

It can be implied, when "Golden" is excluded from the search, there are no beginner friendly items to be made


---


By filtering the search down further, there are more early game accessible items.


```{r Starting_items, echo=FALSE}

spring_or_any_crops_sun_haven <-  crops %>% 
  filter((season == "Spring" | 
          season == "Any") & 
          currency == "Gold") %>% 
  pull(name)  # Pull out the crop names

filtered_foods_sun_haven <- cooked_food %>% 
  mutate(
    has_spring_crop_sun_haven = ingredient_1 %in% spring_or_any_crops_sun_haven | 
                      ingredient_2 %in% spring_or_any_crops_sun_haven | 
                      ingredient_3 %in% spring_or_any_crops_sun_haven) %>% 
  filter(has_spring_crop_sun_haven & 
           currency == "Gold" &
           stat == "Mana")  # Keep only rows where the new column is TRUE

top_10_foods_sun_haven <- filtered_foods_sun_haven %>%
  select(station, item,currency, stat_boost, ingredient_1, ingredient_2, ingredient_3) %>%
  head(10)  # Select the top 10

tibble(top_10_foods_sun_haven)

```

---

# Conclusion 


If the player is starting gameplay, a filtered search looking at recipes with:

 Sun Haven (starting town), Spring

Gives players a large amount of items that can be made at to permanently increase their mana stats.

A more generalized search can help players optimize resource management after first year gameplay.

In both instances, players can figure out farm and storage layout as well as where they would like to focus more of their time to increase the mana stat in order to more efficiently play the game. 
